Energy simulation and analysis of accessory dwelling units: an evolutionary approach

### 2021-06-14 writing/essay_latex/Energy_simulation_and_analysis_ADU.tex

\documentclass[sagev,times,Royal]{sagej}
% add 'doublespace'

\usepackage{moreverb,url}

\usepackage{graphicx}

@@

\section{Introduction}
The United States is amidst an unprecedented housing crisis, stemming from parallel crises: from neoliberal austerity spending cuts towards social benefits to the near-virtual lack of social housing and rent control programs in the United States to the ever-increasing privatization of essentially every aspect of American life\cite{10.2307/26297969}. The result is a rising population of unhoused peoples and the inability for many to become a homeowner or to even afford minimum monthly rent in many cities. Solutions to this dilemma are neither straightforward nor definite. However, designers and architects can only address the symptom-level problems, while advocating towards change directed at the root cause.

@@

@@

These constraints are built into the Grasshopper definition in such a way that the tool requires simply lot extents and the footprint of the existing residential structure to develop the buildable area for any DADU construction. Each DADU is represented as a simple 12' shoebox model with facades oriented  perpendicular to the cardinal directions. Under current Seattle Residential Building Code (2018), minimum R-values for wall and ceiling assemblies are R-21 and R-49, respectively. Light wood frame construction was chosen for all three sites, as the majority of residential construction in the United States and in Seattle specifically falls under this category due to price and ubiquity. For this project, total R-values were set to 26.86, 54.592, and 5.73, for wall, roof, and floor assemblies, respectively. Wall and roof assemblies are detailed in Tables \ref{table:wall-assembly} and \ref{table:roof-assembly}. Floor condition is a standard slab-on-grade with rigid insulation below an 8" concrete slab, finished with carpeting.

% Wall Assembly
\begin{table}[]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{lcccc}
\hline
\multicolumn{1}{|l|}{\textbf{Assembly}} &
  \multicolumn{1}{l|}{\textbf{Notes}} &
  \multicolumn{1}{c|}{\textbf{R-Value}} &
  \multicolumn{1}{l|}{\textbf{Path 1 (Insulation)}} &
  \multicolumn{1}{l|}{\textbf{Path 2 (Framing)}} \\ \hline
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Interior} &
  \multicolumn{1}{c|}{0.68} &
  \multicolumn{1}{c|}{0.68} &
  \multicolumn{1}{c|}{0.68} \\ \hline
\multicolumn{1}{|l|}{Gypsum Board} &
  \multicolumn{1}{c|}{1/2"} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} \\ \hline
\multicolumn{1}{|l|}{Vapor Barrier} &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} \\ \hline
\multicolumn{1}{|l|}{Rigid Insulation} &
  \multicolumn{1}{c|}{4"} &
  \multicolumn{1}{c|}{6} &
  \multicolumn{1}{c|}{24} &
  \multicolumn{1}{c|}{-} \\ \hline
\multicolumn{1}{|l|}{2" x 6" Wood Stud} &
  \multicolumn{1}{c|}{16" o.c.} &
  \multicolumn{1}{c|}{12.31} &
  \multicolumn{1}{c|}{-} &
  \multicolumn{1}{c|}{12.31} \\ \hline
\multicolumn{1}{|l|}{Air Gap} &
  \multicolumn{1}{c|}{1"} &
  \multicolumn{1}{c|}{2.38} &
  \multicolumn{1}{c|}{2.38} &
  \multicolumn{1}{c|}{2.38} \\ \hline
\multicolumn{1}{|l|}{Wood Cladding} &
  \multicolumn{1}{c|}{3/4"} &
  \multicolumn{1}{c|}{0.93} &
  \multicolumn{1}{c|}{0.93} &
  \multicolumn{1}{c|}{0.93} \\ \hline
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Exterior} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} \\ \hline
 &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{\textbf{R-Total:}} &
  \multicolumn{1}{c|}{28.61} &
  \multicolumn{1}{c|}{16.92} \\ \cline{3-5} 
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \textit{x 85\%} &
  \textit{x 15\%} \\
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  24.3185 &
  2.538 \\ \cline{3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{c|}{\textbf{Wall R-Value:}} &
  \multicolumn{2}{c|}{26.86} \\ \cline{3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{l|}{\textbf{Wall U-Value:}} &
  \multicolumn{2}{c|}{0.0372} \\ \cline{3-5} 
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{}
\end{tabular}%
}
\caption{Wall Assembly}
\label{table:wall-assembly}
\end{table}

% Roof Assembly
\begin{table}[]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{lcccc}
\hline
\multicolumn{1}{|l|}{\textbf{Assembly}} &
  \multicolumn{1}{l|}{\textbf{Notes}} &
  \multicolumn{1}{c|}{\textbf{R-Value}} &
  \multicolumn{1}{l|}{\textbf{Path 1 (Insulation)}} &
  \multicolumn{1}{l|}{\textbf{Path 2 (Framing)}} \\ \hline
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Interior} &
  \multicolumn{1}{c|}{0.61} &
  \multicolumn{1}{c|}{0.61} &
  \multicolumn{1}{c|}{0.61} \\ \hline
\multicolumn{1}{|l|}{Gypsum Board} &
  \multicolumn{1}{c|}{1/2"} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} \\ \hline
\multicolumn{1}{|l|}{Vapor Barrier} &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} \\ \hline
\multicolumn{1}{|l|}{Cellulose Insulation} &
  \multicolumn{1}{c|}{Blow-in} &
  \multicolumn{1}{c|}{47} &
  \multicolumn{1}{c|}{47} &
  \multicolumn{1}{c|}{-} \\ \hline
\multicolumn{1}{|l|}{2" x 10" Wood Rafters} &
  \multicolumn{1}{c|}{24" o.c.} &
  \multicolumn{1}{c|}{14.68} &
  \multicolumn{1}{c|}{-} &
  \multicolumn{1}{c|}{14.68} \\ \hline
\multicolumn{1}{|l|}{Rigid Insulation} &
  \multicolumn{1}{c|}{2"} &
  \multicolumn{1}{c|}{10} &
  \multicolumn{1}{c|}{10} &
  \multicolumn{1}{c|}{10} \\ \hline
\multicolumn{1}{|l|}{OSB Sheathing} &
  \multicolumn{1}{c|}{7/16"} &
  \multicolumn{1}{c|}{0.77} &
  \multicolumn{1}{c|}{0.77} &
  \multicolumn{1}{c|}{0.77} \\ \hline
\multicolumn{1}{|l|}{Asphalt Shingles} &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{0.44} &
  \multicolumn{1}{c|}{0.44} &
  \multicolumn{1}{c|}{0.44} \\ \hline
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Exterior} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} \\ \hline
 &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{\textbf{R-Total:}} &
  \multicolumn{1}{c|}{59.44} &
  \multicolumn{1}{c|}{27.12} \\ \cline{3-5} 
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \textit{x 85\%} &
  \textit{x 15\%} \\
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  50.524 &
  4.068 \\ \cline{3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{c|}{\textbf{Wall R-Value:}} &
  \multicolumn{2}{c|}{54.592} \\ \cline{3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{l|}{\textbf{Wall U-Value:}} &
  \multicolumn{2}{c|}{0.0183} \\ \cline{3-5} 
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{}
\end{tabular}%
}
\caption{Roof Assembly}
\label{table:roof-assembly}
\end{table}

\subsection{Energy model and analysis}
Honeybee, part of the open-source Ladybug Tools plugin suite for Grasshopper and Rhino, has become an industry standard for daylighting simulation and energy modeling within architecture and engineering, largely due to its open source nature\cite{mackey2018tool}. Honeybee acts as a bridge between modeled Rhino geometry and the United States Department of Energy's EnergyPlus simulation tool. Modeled geometry is constructed as rooms and zones within Honeybee, offering greater granularity. EnergyPlus operates using various abstractions and simplifications and these are important to note\cite{EnergyPlusTMVersionDocumentation2021}. Each zone and surface is only able to hold one temperature value at a time- each singular value is averaged across the zone or surface. Each DADU simulated is represented as a single zone spanning the entire structure. Alternatively, using four zones and a core instead would have increased resolution of results, but at the cost of much longer simulation times. For building typologies larger than ADUs, this discrepancy between EUI simulation results using one or five (four and a core) zones has been studied\cite{SingleZoneVs2018}. Results showed EUI estimates experienced 4.23\% variance on average for cities tested. Further, for Seattle specifically, results varied by only 2.12\%.

Similarly, trees are represented as simple cylindrical solids, in order to keep energy simulation speed quick and to reduce the time necessary to reach an optimal solution. In initial tests, trees were represented as spherical meshes created using Grasshopper. These more-detailed trees varied in opaque triangulated mesh coverage to simulate foliage cover and to more accurately cast shadows. It is important to note that with access to greater computing power it could become reasonable to represent and simulate trees in the original format. Together with other context, including the associated residence and nearby residences capable of projecting shadows onto the DADU, the tree models were assigned as shades in the Honeybee model.

The final input required for the Honeybee/EnergyPlus model is a weather file, in .EPW (EnergyPlus Weather File) format. These files contain yearly climate data for a geographic location; in this case data was collected at the King County International Airport - Boeing Field in Seattle, Washington. The American Society of Heating, Refrigerating, and Air-Conditioning Engineers (ASHRAE) defines climate zones for use with EnergyPlus and other tools/calculations. Seattle falls within the ASHRAE 169-2006 standard 4C climate, defined as \textit{Mixed - Marine}. This climate type is utilized within the Grasshopper script to define the wood frame construction type for the Seattle climate. EPW files are obtainable freely at \textit{EnergyPlus.net}, the United States Department of Energy's official EnergyPlus website.

Output data consists of the final, optimized site EUI value for each DADU as a sum value of cooling, heating, lighting, equipment, and hot water EUIs. Lighting, equipment, and hot water are all held constant at 1.923 kBTU/ft$^2$, 9.645 kBTU/ft$^2$, and 14.295 kBTU/ft$^2$, respectively.

\subsection{Genetic algorithm}
Genetic algorithms operate using logic that mimics biological evolution to optimize a value. Fitness functions are the means by which to objectively evaluate the strength of individual designs. In this case, the fitness value minimized is the resultant EUI value corresponding to each set of window-to-wall ratios. Work was initially done using a purely Python-based GA script, but later pivoted to utilizing Galapagos, a genetic solver plugin that ships with Grasshopper. Utilizing Grasshopper and Galapagos offers a ‘sandbox’ environment to begin to understand genetic algorithms and to arrive at tangible design solutions faster than using a home-brewed algorithm. Further, Galapagos offers a simple user interface and a more direct integration within Grasshopper at the cost of advanced options. These options however were not necessary for the level of optimization required within this project. Galapagos accepts Grasshopper slider components as input, with the domain set independently for each slider. As each DADU is reduced to a shoebox model, each facade is governed by one individual WWR slider, each with domain $\lbrace x \vert 0 \leq x \leq 0.95 \rbrace$.

Each Galapagos optimization was run twice for each site as a means to double check that the first result was not simply a local minimum. The evolutionary solver input panel was set as follows:

@@

\section{Results}
\begin{figure}[h!]
\centering
\includegraphics{site1.pdf}
\caption{Site 1: 961 20th Ave, Seattle WA | DADU floor area: 1000 ft$^2$}
\label{site1-plan}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{site2.pdf}
\caption{Site 2: 328 17th Ave, Seattle WA | DADU floor area: 520 ft$^2$}
\label{site2-plan}
\end{figure}

Site selection was primarily driven by orientation between DADU location and existing residences, with each site in a differing neighborhood of Seattle. The Central District, Minor, and Madrona neighborhoods all lie east of downtown Seattle, greatly uphill. Neighborhoods differ slightly in density, street width, and demographics but all chosen sites are within identical SF5000 zoning. Site 1 is located at 961 20th Avenue in the Central District and the DADU is bordered directly by existing structures to the north and east. This DADU is the largest explored, reaching the maximum allowable floor area by single family code\cite{ADUniverseADURules}. Site 2 resides at 328 17th Avenue in Minor and its DADU structure is adjacent to the east of the existing home. This site is unique out of the three, as there is an additional existing structure located on the lot, being a small storage shed to the south-east. Finally, site 3, located at 3413 East Pine Street within Madrona consists of the existing residence facing the street to the north, with DADU location to the south. Neighboring residences to the east and southeast account for the majority of shading effect.

\begin{figure}[h!]
\centering
\includegraphics{site3.pdf}
\caption{Site 3: 3413 E Pine St, Seattle WA | DADU floor area: 680 ft$^2$}
\label{site3-plan}
\end{figure}

%TODO Add data visualizations of results
%TODO additional simplified plans or renderings of DADUs and sites
%TODO eui output breakdown and total, point out how only cooling and heating truly vary
%TODO Limitations of Galapagos/Grasshopper workflow

\section{Conclusion}
%TODO Add main conclusion section, user ability to override window sizing and placement- feedback loop?
Looking forward, the intention is to replace the computationally-expensive EnergyPlus simulation with a machine learning model that can predict EUI performance. This technique is essentially  surrogate modeling; that is, a means to approximate/predict the energy performance without doing the thermodynamics calculations required to return a true value. Machine learning algorithms require vast troves of data to learn from in order to increase accuracy past an acceptable threshold. This tool generates the optimized energy simulation data, which in turn becomes the training dataset. Assuming the resultant tool could be hosted on the web, this theoretically increases the rate of adoption by lowering the requirement to utilize the tool.

>>>>

\documentclass[sagev,times,Review,doublespace]{sagej}
% add 'doublespace'

\usepackage{moreverb,url,graphicx}

@@

\section{Introduction}
The United States is amidst an unprecedented housing crisis, stemming from parallel crises: from neoliberal austerity spending cuts towards social benefits to the near-virtual lack of social housing and rent control programs in the US to the ever-increasing privatization of essentially every aspect of American life\cite{10.2307/26297969}. The result is a rising population of unhoused peoples and the inability for many to become a homeowner or to even afford minimum monthly rent in many cities. Solutions to this dilemma are neither straightforward nor definite. However, designers and architects can only address the symptom-level problems, while advocating towards change directed at the root cause.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=4in]{3d-view.png}
\caption{Isometric view of DADU, demonstrating WWR representation}
\label{3d-view}
\end{figure}

@@

These constraints are built into the Grasshopper definition in such a way that the tool requires simply lot extents and the footprint of the existing residential structure to develop the buildable area for any DADU construction. Each DADU is represented as a simple 12' shoebox model with facades oriented  perpendicular to the cardinal directions. Under current Seattle Residential Building Code (2018), minimum R-values for wall and ceiling assemblies are R-21 and R-49, respectively. Light wood frame construction was chosen for all three sites, as the majority of residential construction in the US and in Seattle specifically falls under this category due to price and ubiquity. For this project, total R-values were set to 26.86, 54.592, and 5.73, for wall, roof, and floor assemblies, respectively. Wall and roof assemblies are detailed in Tables \ref{table:wall-assembly} and \ref{table:roof-assembly}. Floor condition is a standard slab-on-grade with rigid insulation below an 8" concrete slab, finished with carpeting.

% Wall Assembly
\begin{table}[h!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Assembly} &
  \multicolumn{1}{l}{\textbf{Notes}} &
  \textbf{R (\(\frac{^{\circ}F\,ft^2\,hr}{BTU}\))} &
  \multicolumn{1}{l}{\textbf{Path 1} (Insulation)} &
  \multicolumn{1}{l}{\textbf{Path 2} (Framing)} \\ \midrule
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Interior} &
  \multicolumn{1}{c|}{0.68} &
  \multicolumn{1}{c|}{0.68} &
  \multicolumn{1}{c|}{0.68} \\ \midrule
\multicolumn{1}{|l|}{Gypsum Board} &
  \multicolumn{1}{c|}{1/2"} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} \\ \midrule
\multicolumn{1}{|l|}{Vapor Barrier} &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} \\ \midrule
\multicolumn{1}{|l|}{Rigid Insulation} &
  \multicolumn{1}{c|}{4"} &
  \multicolumn{1}{c|}{6} &
  \multicolumn{1}{c|}{24} &
  \multicolumn{1}{c|}{-} \\ \midrule
\multicolumn{1}{|l|}{2" x 6" Wood Stud} &
  \multicolumn{1}{c|}{16" o.c.} &
  \multicolumn{1}{c|}{12.31} &
  \multicolumn{1}{c|}{-} &
  \multicolumn{1}{c|}{12.31} \\ \midrule
\multicolumn{1}{|l|}{Air Gap} &
  \multicolumn{1}{c|}{1"} &
  \multicolumn{1}{c|}{2.38} &
  \multicolumn{1}{c|}{2.38} &
  \multicolumn{1}{c|}{2.38} \\ \midrule
\multicolumn{1}{|l|}{Wood Cladding} &
  \multicolumn{1}{c|}{3/4"} &
  \multicolumn{1}{c|}{0.93} &
  \multicolumn{1}{c|}{0.93} &
  \multicolumn{1}{c|}{0.93} \\ \midrule
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Exterior} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} \\ \midrule
 &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{\textbf{R$_{total}$}} &
  \multicolumn{1}{c|}{28.61} &
  \multicolumn{1}{c|}{16.92} \\ \cmidrule(l){3-5} 
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \textit{x 85\%} &
  \textit{x 15\%} \\
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  24.3185 &
  2.538 \\ \cmidrule(l){3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{c|}{\textbf{R$_{wall}$}} &
  \multicolumn{2}{c|}{26.86} \\ \cmidrule(l){3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{c|}{\textbf{U$_{wall}$}} &
  \multicolumn{2}{c|}{0.0372} \\
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} \\ \bottomrule
\end{tabular}%
}
\caption{Wall Assembly}
\label{table:wall-assembly}
\end{table}

% Roof Assembly
\begin{table}[h!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Assembly} &
  \multicolumn{1}{l}{\textbf{Notes}} &
  \textbf{R (\(\frac{^{\circ}F\,ft^2\,hr}{BTU}\))} &
  \multicolumn{1}{l}{\textbf{Path 1} (Insulation)} &
  \multicolumn{1}{l}{\textbf{Path 2} (Framing)} \\ \midrule
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Interior} &
  \multicolumn{1}{c|}{0.61} &
  \multicolumn{1}{c|}{0.61} &
  \multicolumn{1}{c|}{0.61} \\ \midrule
\multicolumn{1}{|l|}{Gypsum Board} &
  \multicolumn{1}{c|}{1/2"} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} &
  \multicolumn{1}{c|}{0.45} \\ \midrule
\multicolumn{1}{|l|}{Vapor Barrier} &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} &
  \multicolumn{1}{c|}{0} \\ \midrule
\multicolumn{1}{|l|}{Cellulose Insulation}  & \multicolumn{1}{c|}{Blow-in}  & \multicolumn{1}{c|}{47}    & \multicolumn{1}{c|}{47}   & \multicolumn{1}{c|}{-}     \\ \midrule
\multicolumn{1}{|l|}{2" x 10" Wood Rafters} & \multicolumn{1}{c|}{24" o.c.} & \multicolumn{1}{c|}{14.68} & \multicolumn{1}{c|}{-}    & \multicolumn{1}{c|}{14.68} \\ \midrule
\multicolumn{1}{|l|}{Rigid Insulation} &
  \multicolumn{1}{c|}{2"} &
  \multicolumn{1}{c|}{10} &
  \multicolumn{1}{c|}{10} &
  \multicolumn{1}{c|}{10} \\ \midrule
\multicolumn{1}{|l|}{OSB Sheathing}         & \multicolumn{1}{c|}{7/16"}    & \multicolumn{1}{c|}{0.77}  & \multicolumn{1}{c|}{0.77} & \multicolumn{1}{c|}{0.77}  \\ \midrule
\multicolumn{1}{|l|}{Asphalt Shingles} &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{0.44} &
  \multicolumn{1}{c|}{0.44} &
  \multicolumn{1}{c|}{0.44} \\ \midrule
\multicolumn{1}{|l|}{Air Film} &
  \multicolumn{1}{c|}{Exterior} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} &
  \multicolumn{1}{c|}{0.17} \\ \midrule
 &
  \multicolumn{1}{c|}{} &
  \multicolumn{1}{c|}{\textbf{R$_{total}$}} &
  \multicolumn{1}{c|}{59.44} &
  \multicolumn{1}{c|}{27.12} \\ \cmidrule(l){3-5} 
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \textit{x 85\%} &
  \textit{x 15\%} \\
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  50.524 &
  4.068 \\ \cmidrule(l){3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{c|}{\textbf{R$_{wall}$}} &
  \multicolumn{2}{c|}{54.592} \\ \cmidrule(l){3-5} 
 &
  \multicolumn{1}{l|}{} &
  \multicolumn{1}{c|}{\textbf{U$_{wall}$}} &
  \multicolumn{2}{c|}{0.0183} \\
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} \\ \bottomrule
\end{tabular}%
}
\caption{Roof Assembly}
\label{table:roof-assembly}
\end{table}

\subsection{Energy model and analysis}
Honeybee, part of the open-source Ladybug Tools plugin suite for Grasshopper and Rhino, has become an industry standard for daylighting simulation and energy modeling within architecture and engineering, largely due to its open source nature\cite{mackey2018tool}. Honeybee acts as a bridge between modeled Rhino geometry and the US Department of Energy's EnergyPlus simulation tool. Modeled geometry is constructed as rooms and zones within Honeybee, offering greater granularity. EnergyPlus operates using various abstractions and simplifications and these are important to note\cite{EnergyPlusTMVersionDocumentation2021}. Each zone and surface is only able to hold one temperature value at a time- each singular value is averaged across the zone or surface. Each DADU simulated is represented as a single zone spanning the entire structure. Alternatively, using four zones and a core instead would have increased resolution of results, but at the cost of much longer simulation times. For building typologies larger than ADUs, this discrepancy between EUI simulation results using one or five (four and a core) zones has been studied\cite{SingleZoneVs2018}. Results showed EUI estimates experienced 4.23\% variance on average for cities tested. Further, for Seattle specifically, results varied by only 2.12\%.
Similarly, trees are represented as simple cylindrical solids, in order to keep energy simulation speed quick and to reduce the time necessary to reach an optimal solution. In initial tests, trees were represented as spherical meshes created using Grasshopper. These more-detailed trees varied in opaque triangulated mesh coverage to simulate foliage cover and to more accurately cast shadows. It is important to note that with access to greater computing power it could become reasonable to represent and simulate trees in the original format. Together with other context, including the associated residence and nearby residences capable of projecting shadows onto the DADU, the tree models were assigned as shades in the Honeybee model.

The final input required for the Honeybee/EnergyPlus model is a weather file, in .EPW (EnergyPlus Weather File) format. These files contain yearly climate data for a geographic location; in this case data was collected at the King County International Airport - Boeing Field in Seattle, Washington. The American Society of Heating, Refrigerating, and Air-Conditioning Engineers (ASHRAE) defines climate zones for use with EnergyPlus and other tools/calculations. Seattle falls within the ASHRAE 169-2006 standard 4C climate, defined as \textit{Mixed - Marine}. This climate type is utilized within the Grasshopper script to define the wood frame construction type for the Seattle climate. EPW files are obtainable freely at \textit{EnergyPlus.net}, the US Department of Energy's official EnergyPlus website. Output data consists of the final, optimized site EUI value for each DADU as a sum value of cooling, heating, lighting, equipment, and hot water EUIs. Lighting, equipment, and hot water are all held constant at 1.923 kBTU/ft$^2$, 9.645 kBTU/ft$^2$, and 14.295 kBTU/ft$^2$, respectively.

\subsection{Genetic algorithm}
Genetic algorithms operate using logic that mimics biological evolution to optimize a value. Fitness functions are the means by which to objectively evaluate the strength of individual designs. In this case, the fitness value minimized is the resultant EUI value corresponding to each set of window-to-wall ratios. Work was initially done using a purely Python-based GA script, but later pivoted to utilizing Galapagos, a genetic solver plugin that ships with Grasshopper. Utilizing Grasshopper and Galapagos offers a ‘sandbox’ environment to begin to understand genetic algorithms and to arrive at tangible design solutions faster than using a home-brewed algorithm. Further, Galapagos offers a simple user interface and a more direct integration within Grasshopper at the cost of advanced options. However, these options were not necessary for the level of optimization required within this project. Galapagos accepts Grasshopper slider components as input, with the domain set independently for each slider. As each DADU is reduced to a shoebox model, each facade is governed by one individual WWR slider, each with domain $\lbrace x \vert 0 \leq x \leq 0.95 \rbrace$. Each Galapagos optimization was run five times for each site as a means to  check for outliers and not simply a local minimum. The evolutionary solver input panel was set as follows:

@@

\begin{figure}[h!]
\centering
\includegraphics{site1.pdf}
\caption{Site 1 (Central District): 961 20th Avenue | DADU floor area: 1000 ft$^2$}
\label{site1-plan}
\end{figure}

\section{Results}
Site selection was primarily driven by orientation between DADU location and existing residences, with each site in a differing neighborhood of Seattle. The Central District, Minor, and Madrona neighborhoods all lie east of downtown Seattle, greatly uphill. Neighborhoods differ slightly in density, street width, and demographics but all chosen sites are within identical SF5000 zoning. Site 1 is located at 961 20th Avenue in the Central District and the DADU is bordered directly by existing structures to the north and east. This DADU is the largest explored, reaching the maximum allowable floor area of 1000 ft$^2$, as limited by single family code\cite{ADUniverseADURules}. Site 2 resides at 328 17th Avenue in Minor and its DADU structure is adjacent to the east of the existing home. This site is unique out of the three, as there is an additional existing structure located on the lot, being a small storage shed to the south-east. DADU footprint for site 2 totals 520 ft$^2$. Finally, site 3, located at 3413 East Pine Street within Madrona consists of the existing residence facing the street to the north, with DADU location to the south. Gross floor area of this DADU structure is 680 ft$^2$. Neighboring residences to the east and southeast account for the majority of shading effect. One future consideration is to allow for override to WWR domain, either automatically or manually selected by user. For example, let's say the DADU at site 3 found a value of 35\% for the southern facade. This may be optimal, but the majority of owners likely would opt to avoid windows facing directly into their neighbors private spaces of their dwelling. The genetic algorithm could contain a few toggles for override.

\begin{figure}[h!]
\centering
\includegraphics{site2.pdf}
\caption{Site 2 (Minor): 328 17th Avenue | DADU floor area: 520 ft$^2$}
\label{site2-plan}
\end{figure}

Averaged optimal total site EUI was found to differ by less than 4 kBTU/ft$^2$ between all three sites. Total EUI was calculated to be 62.675 kBTU/ft$^2$, 61.207 kBTU/ft$^2$, and 64.059 kBTU/ft$^2$ for sites 1-3, respectively. Heating, on average, constituted for about 50\% of total EUI, while cooling accounted for only about 9\% of total site EUI on average. Optimal WWR values were found to be greatly similar between sites, regardless of context and orientation to existing residences. North, west, and east WWR values were typically found to lower EUI when lowered almost to zero. On the other hand, the south WWR approached .25 on average. North WWR was found to fall between 0 and 0.18, with an average value of 0.08 percent glazed to opaque. East and west WWRs typically fell between 0 and 0.11, with the majority of Galapagos runs ending with zero glazing on the east and west facades. Curiously, the lowest EUI found out of any runs was located at site 2 in Minor, with WWRs of 0.06 north, 0.09 east, 0.10 south, and 0 west. This combination of window to wall ratios stands out as it was simultaneously the only resultant where north, east, and south ratios are almost identical and non-zero.

\begin{figure}[h!]
\centering
\includegraphics{site3.pdf}
\caption{Site 3 (Madrona): 3413 East Pine Street | DADU floor area: 680 ft$^2$}
\label{site3-plan}
\end{figure}

Table 3 displays the averaged results by site, as well as overall. Comparing these optimal values to a worst case and an educated guess demonstrates the value in using such a relatively simple design tool like Galapagos- one which is already bundled with Rhinoceros software (as of version 6). A worst case result was calculated for site 3 by maximizing the EUI using Galapagos. Total site EUI was found to be 91.048 kBTU/ft$^2$, a 42.13\% increase over the optimal solution's total site EUI value of 64.059 kBTU/ft$^2$. North, east, south, and west WWRs were set by the solver to 0.79, 0.95, 0.95, and 0.90, respectively. An educated guess consisting of WWR settings of 0.06, 0.18, 0.59, and 0.18, in the aforementioned order leads to a total site EUI of 69.643 kBTU/ft$^2$. In comparison to the optimal WWR arrangement, this results in only a 8.717\% EUI increase. This result can be taken to mean that even for seasoned designers, this tool can still offer nearly 10\% greater energy efficiency, as well as a simple way to verify hand calculations or other means of estimating.

\begin{table}[h!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lcccccc@{}}
\toprule
 &
  \multicolumn{6}{c}{\textbf{Energy Use Intensity (kBTU/ft$^2$)}} \\ \midrule
\multicolumn{1}{|c|}{Site} &
  \multicolumn{1}{c|}{Cooling} &
  \multicolumn{1}{c|}{Heating} &
  \multicolumn{1}{c|}{Lighting} &
  \multicolumn{1}{c|}{Equipment} &
  \multicolumn{1}{c|}{Hot Water} &
  \multicolumn{1}{c|}{Total} \\ \midrule
\multicolumn{1}{|l|}{961 20th Ave} &
  \multicolumn{1}{c|}{4.169} &
  \multicolumn{1}{c|}{32.643} &
  \multicolumn{1}{c|}{1.923} &
  \multicolumn{1}{c|}{9.645} &
  \multicolumn{1}{c|}{14.295} &
  \multicolumn{1}{c|}{62.675} \\ \midrule
\multicolumn{1}{|l|}{328 17th Ave} &
  \multicolumn{1}{c|}{7.657} &
  \multicolumn{1}{c|}{27.688} &
  \multicolumn{1}{c|}{1.923} &
  \multicolumn{1}{c|}{9.645} &
  \multicolumn{1}{c|}{14.295} &
  \multicolumn{1}{c|}{61.207} \\ \midrule
\multicolumn{1}{|l|}{3413 E Pine St} &
  \multicolumn{1}{c|}{5.039} &
  \multicolumn{1}{c|}{33.157} &
  \multicolumn{1}{c|}{1.923} &
  \multicolumn{1}{c|}{9.645} &
  \multicolumn{1}{c|}{14.295} &
  \multicolumn{1}{c|}{64.059} \\ \midrule
 &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} &
  \multicolumn{1}{l}{} \\
\textbf{Average} &
  5.621 &
  31.162 &
  1.923 &
  9.645 &
  14.295 &
  62.647 \\ \bottomrule
\end{tabular}%
}
\label{results-table}
\caption{Optimized EUI Results}
\end{table}
